Blas\'e3D

### 2023-11-07 paper/paper2/ms.tex
Pair writing with sujay

\section{Introduction}
\blindtext

>>>>

\section{Introduction}

\subsection{General spectroscopy ideas}

\textbf{what do we want}\\
Key goal: semi-empirical models-- a model that can continuously learn from and adapt to data.  Each new observed data spectrum informs changes to our preconceived theories of how stellar atmospheres produce spectra.  We seek model flexibility where we expect there to be deficiencies in these theories, and rigidity where we expect our theories to be most robust.

\textbf{Why is that hard}\\

Comparison to \citet{czekala15}.  Describe limitation of pre-designating 1 grid point.

blasePaper1 describes a way to overcome this limitation by building up a so-called ``heatmap'' of line properties.  The realization of such a function enables a key capability: semi-empirical models.
This paper implements ths
